A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-18 manuscript.Rmd
added abstract removed toc

---
title: "A Hitchhiker's Guide to Reproducible Research" # replace with something serious
author: Aaron Peikert and Andreas M. Brandmaier 
output:
  bookdown::pdf_document2:
    keep_tex: TRUE
repro:
  packages:
    - tidyverse
    - usethis
    - gert
    - aaronpeikert/repro@7bfaf98
    - here
    - rstudio/webshot2@f62e743
    - targets
    - renv
    - slider
    - patchwork
    - knitr
    - pander
    - lavaan
    - furrr
    - future.batchtools
  scripts:
    - R/simulation.R
    - R/simulation_funs.R
    - R/link.R
csl: apa7.csl
numbered_headings: true
bibliography: ["references.bib", "packages.bib"]
---

@@

```{r}
# define a ürint method for objects of the class data.frame
knit_print.data.frame = function(x, ...) {
  res = paste(c('', '', kable(x)), collapse = '\n')
  asis_output(res)
}
# register the method
registerS3method("knit_print", "data.frame", knit_print.data.frame)
```

@@

The `repro` package is particularly well-suited for computationally intensive data analyses and simulations that  are to be run on distributed computing environments.
By using containers, `repro` ensures identical execution across platforms and thus guarantees that a data analysis or simulation that was designed and tested on a local computer will be executed in the identical manner on a remote machine or various remote machines across an entire computing cluster.
Thereby, the repro package makes massive parallel computing in heterogeneous computing environments less error-prone while ensuring the full documentation of all computational steps taken — even if some or all of them were run in parallel on distributed platforms.
Alone the sheer data size often warrants distributed computing, e.g. the European Bioinformatics Institute stores more than 120 Petabyte of publicly accessible data [@cookEuropeanBioinformaticsInstitute2018], single FMRI studies quickly amount to hundreds of Gigabyte[^openneuro] and even purely behavioral data like from the moral machine experiment [>10GB, @awadMoralMachineExperiment2018] can become to big to handle .

@@

As default, `repro` uses Docker, which is the defacto standard for cloud computing, as a container solution.
However, Docker requires administrator rights for execution.
Whereas this is no issue on most modern cloud computing infrastructures, it is often an issue in classic HPC environments.
Singularity is an alternative solution.
It was designed to run without administratot rights, while maintaining full compatibility with Docker images.
If you already have a Docker image, you can choose if you want to run this image with Docker or with Singularity.
Importantly, this choice does not affect how code is executed inside the container.
Like with Docker, the default `Makefile` generated by `repro` comes with a mechanism to automatically send all commands to Singularity.
To reproduce an analysis with Singularity, simple add the parameter `SINGULARITY=TRUE` as follows:

@@

## Reproduce a Project

@@

Ideally, you have a statement in the README that contains a few steps to reproduce the project, where most steps are automatic and standardized.
This statement should also note the required software.
Figure \@ref(fig:readme) shows `r link("https://github.com/aaronpeikert/repro-tutorial#how-to-reproduce-this-manuscript", "the reproduction statement of this project")`.
E.g. you can download any git repository with these commands:

@@

Projects that combine Make and Docker then can usually be reproduced with:

@@

Because you probably want to reproduce your own project each time something changes, you will often want to reproduce evertyhting.
The `repro`-package contains a function designed for that purpose:

@@

If you have written a [Preregistration as Code] you can swap the data file and reproduce the project.
In fact, till after we preregistered the study `r link("https://github.com/aaronpeikert/repro-tutorial/releases/tag/ v0.0.1-preregistration", "preregistration")` were the results below based on simulated data.
Only after we preregistered the whole manuscript and upon submission, they were based on actual data from https://openpsychometrics.org/_rawdata/.

@@

<!-- Hands-on: check changed hash -->
A prerequisite to reproducibility is the availability of code and data.
We use containers to guarantee that all code components are available and work as expected.
Ideally, all data is also stored in the repository [for a more comprehensive argument for publishing data see @vanlissa2020worcs], but this is not always feasible.
Sometimes it is just the required storage capacity that exceeds what Git can handle (Git gets slow around more than 100mb).
In such case we strongly recommend using [DataLad [@DataladDatalad2021]](http://handbook.datalad.org/en/latest/)[^datalad] or the below procedure to guarantee that the data has not changed.
In practice, however, there are various reasons, which may prohibit you from making your data publicly available, for example legal or regulatory or privacy concerns.
You may find yourself in a situation where you can make the data only available on request.
A major threat to reproducibility is that the data has changed in the meantime or multiple versions are circulating and it is not exactly clear what version was used originally.
To at least check that the data was not changed, we suggest to provide a so called "hash", which is a cryptographic fingerprint.
If the data changes, so does its fingerprint or hash.
The user can therefore compare if the data they have received is the same that was used in the original publication, as long as the original publication does contain the hash of the data.

To verify the data integrity, you can include a line of code after reading the data that looks like this:

@@

We employed the same mechanism for our simulation to verify that the simulation is really reproducible[^simhash].

@@

An compromise between making the data publicly available and keeping it closed is to publish synthetic data [@vanlissa2020worcs].
Such approach tries to recreate the marginal distribution and bivariate relationships in simulated data, e.g. with the R package `synthpop`[@nowokSynthpopBespokeCreation2016].
The results of such data should generally not be interpreted.
However, synthetic data provides an opportunity for readers to test if a project is in principle reproducible, even though they have no access to the data.

>>>>

---
title: "A Hitchhiker's Guide to Reproducible Research" # replace with something serious
author: Aaron Peikert and Andreas M. Brandmaier 
output:
  bookdown::pdf_document2:
    keep_tex: TRUE
    toc: FALSE
repro:
  packages:
    - tidyverse
    - usethis
    - gert
    - aaronpeikert/repro@7bfaf98
    - here
    - rstudio/webshot2@f62e743
    - targets
    - renv
    - slider
    - patchwork
    - knitr
    - pander
    - lavaan
    - furrr
    - future.batchtools
  scripts:
    - R/simulation.R
    - R/simulation_funs.R
    - R/link.R
csl: apa7.csl
numbered_headings: true
bibliography: ["references.bib", "packages.bib"]
abstract:
  Computational reproducibility is the ability to obtain identical results from the *same* data with the *same* computer code. It is a building block for transparent and cumulative science because it enables other researchers, on other computers and later in time, to reproduce and thus understand how results came about while, at the same time, it avoids a variety of errors that may lead to erroneous reporting of statistical and computational results. In this tutorial, we demonstrate how the R package `repro` supports researchers in creating fully computationally reproducible research projects with a focus on current Open Science practices; starting from sketching the research proposal, over preregistering an analysis as executable code with simulated data, until the creation and dissemination of the final scientific report. 
---

@@

```{r echo=FALSE}
# define a ürint method for objects of the class data.frame
knit_print.data.frame = function(x, ...) {
  res = paste(c('', '', kable(x)), collapse = '\n')
  asis_output(res)
}
# register the method
registerS3method("knit_print", "data.frame", knit_print.data.frame)
```

@@

The `repro` package is particularly well-suited for computationally intensive data analyses and simulations that  are to run on distributed computing environments.
Through the use of containers, `repro` ensures identical execution across platforms, guaranteeing that a given data analysis or simulation designed and tested on a local machine will execute identically on a remote machine or multiple different remote machines across an entire computing cluster.
Thereby, the repro package makes massive parallel computing in heterogeneous computing environments less error-prone while ensuring the full documentation of all computational steps taken — even if some or all of them were run in parallel on distributed platforms.
The sheer volume of data often necessitates distributed computing, e.g. the European Bioinformatics Institute stores more than 120 Petabyte of publicly accessible data [@cookEuropeanBioinformaticsInstitute2018], single FMRI studies quickly amount to hundreds of Gigabyte[^openneuro] and even purely behavioral data like those from the moral machine experiment [>10GB, @awadMoralMachineExperiment2018] can become too large to be handled by a single local computer.

@@

As default container solution, `repro` uses Docker, which is a widely adopted standard for cloud computing.
However, Docker requires administrator rights for execution.
Whereas this is no issue on most modern cloud computing infrastructures, it is often an issue in classic HPC environments.
Singularity is an alternative solution.
It was designed to run without administrator rights, while maintaining full compatibility with Docker images.
If you already have a Docker image, you can choose if you want to run this image with Docker or with Singularity.
Importantly, this choice does not affect how code is executed inside the container.
Like with Docker, the default `Makefile` generated by `repro` comes with a mechanism to automatically send all commands to Singularity.
To reproduce an analysis with Singularity, simple add the parameter `SINGULARITY=TRUE` as follows:

@@

## Reproducing a Project

@@

Ideally, you have a statement in the README that contains a few steps to reproduce the project, where most steps are automatic and standardized.
This statement should also note the required software.
Figure \@ref(fig:readme) shows `r link("https://github.com/aaronpeikert/repro-tutorial#how-to-reproduce-this-manuscript", "the reproduction statement of this project")`.
For example, you can download any git repository with these commands:

@@

Projects that combine Make and Docker and adhere to the standard proposed by @Peikert2019 can be reproduced with:

@@

Because you probably want to reproduce your own project each time something changes, you will often want to reproduce everything.
The `repro`-package contains a function designed for that purpose:

@@

If you have written a [Preregistration as Code] you can add the real data file to the project and reproduce the entire project with this single command.
In fact, until after we preregistered the study `r link("https://github.com/aaronpeikert/repro-tutorial/releases/tag/ v0.0.1-preregistration", "preregistration")` were the results below based on simulated data.
Only after we preregistered the whole manuscript and upon submission, they were based on actual data from https://openpsychometrics.org/_rawdata/.

@@

<!-- Hands-on: check changed hash -->
A prerequisite to reproducibility is the permanent availability of both code and data.
We use containers to guarantee that all code components are available and work as expected.
Ideally, all data are also stored in the repository [for a more comprehensive argument for publishing data see @vanlissa2020worcs], but this is not always feasible.
Sometimes it is just the required storage capacity that exceeds what Git can handle (Git gets slow around more than 100mb).
In such case we strongly recommend using [DataLad [@DataladDatalad2021]](http://handbook.datalad.org/en/latest/)[^datalad] or the below procedure to guarantee that the data has not changed.
In practice, however, there are various reasons, which may prohibit you from making your data publicly available, for example legal or regulatory or privacy concerns.
You may find yourself in a situation where you can make the data only available on request.
A major threat to reproducibility is that the data has changed in the meantime or multiple versions are circulating and it is not exactly clear what version was used originally.
To at least check that the data was not changed, we suggest to provide a so called "hash", which is a cryptographic fingerprint.
If the data changes, so does its fingerprint or hash.
The user can therefore compare if the data they have received is the same that was used in the original publication, as long as the original publication does contain the hash of the data.

To verify data integrity, you can include a line of code after reading the data that looks like this:

@@

We employed the same mechanism for our simulation to verify that the simulation is indeed reproducible[^simhash].

@@

A compromise between making the data publicly available and keeping it closed is the publication of synthetic data [@vanlissa2020worcs].
Synthetic data are an attempt to recreate the marginal distribution and bivariate relationships in simulated data. The R package `synthpop`[@nowokSynthpopBespokeCreation2016] provides functions to generate synthetic data .
Of course, the results of such synthetic data should generally not be interpreted but are rather meant to illustrate the workings and the structure of the output of a given data analysis.
Also, synthetic data provides an opportunity for readers to test if a project is in principle reproducible, even though they have no access to the data.
